Interactive Checks for Coordination Avoidance

### 2019-08-15 doc/vldb_slides/iconfluence.tex
Added invariant confluence definitions.

\usepackage{amsmath}
\usepackage{centernot}
\usepackage{etoolbox}
\usepackage{mathtools}
\usepackage{python}
\usepackage{slides}
\usepackage{stmaryrd}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{backgrounds}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}

@@

{\input{sections/four_wise_men.tex}}
{\input{sections/bank_example.tex}}
\end{document}

>>>>

\usepackage{amsmath}
\usepackage{centernot}
\usepackage{etoolbox}
\usepackage{invariantconfluence}
\usepackage{mathpartir}
\usepackage{mathtools}
\usepackage{pervasives}
\usepackage{python}
\usepackage{slides}
\usepackage{stmaryrd}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{backgrounds}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}

@@

{\input{sections/four_wise_men.tex}}
{\input{sections/bank_example.tex}}
{\input{sections/iconfluence.tex}}
{\input{sections/iclosure.tex}}
{\input{sections/decision_procedure.tex}}
{\input{sections/segmented_iconfluence.tex}}
{\input{sections/evaluation.tex}}
\end{document}
